Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-11-18 bbbq_article_issue_157/results.tex
Indeed, '(' is a round bracket, not a round brace, thanks Geert

% latex table generated in R 4.1.1 by xtable 1.8-4 package
% Sun Nov 14 19:33:23 2021
\begin{table}[ht]
\centering
\begin{tabular}{lll}
  \hline
MHC class & Dataset & n \\ 
  \hline
I & iedb\_mhc\_ligand & 22.28\% (1789/8030) \\ 
  I & iedb\_t\_cell & 35.91\% (93/259) \\ 
  II & iedb\_mhc\_ligand & 10.46\% (73/698) \\ 
  II & iedb\_t\_cell &  6.66\% (42/631) \\ 
   \hline
\end{tabular}
\caption{Percentage of epitopes derived from a TMH for epitopes taken from the IEDB, for two different types of assays:  an MHC ligand assay, as well as a T cell assay.  The values between braces show the the number of epitopes that were predicted to overlapping with a TMH per all epitopes that could be uniquely mapped to the representative human reference proteome.} 
\label{tab:elution}
\end{table}

>>>>

% latex table generated in R 4.1.1 by xtable 1.8-4 package
% Sun Nov 14 19:33:23 2021
\begin{table}[ht]
\centering
\begin{tabular}{lll}
  \hline
MHC class & Dataset & n \\ 
  \hline
I & iedb\_mhc\_ligand & 22.28\% (1789/8030) \\ 
  I & iedb\_t\_cell & 35.91\% (93/259) \\ 
  II & iedb\_mhc\_ligand & 10.46\% (73/698) \\ 
  II & iedb\_t\_cell &  6.66\% (42/631) \\ 
   \hline
\end{tabular}
\caption{Percentage of epitopes derived from a TMH for epitopes taken from the IEDB, for two different types of assays:  an MHC ligand assay, as well as a T cell assay.  The values between brackets show the the number of epitopes that were predicted to overlapping with a TMH per all epitopes that could be uniquely mapped to the representative human reference proteome.} 
\label{tab:elution}
\end{table}
